---
output: pdf_document
---
HS - 616 Questions week-wise
================================================================
author: Lakshmi Arbatti

date: 01/31/2015



### Lecture 1a  


If x <- 1:4 and y <- 5:8 what is the output of x + y ?

* A vector with values 6 8 10 12
* A numeric integer with value 6
* A numeric integer with values 6 8 10 12
* Running the statement gives an error


### Lecture 1b  

What is the class() of the vector 'var' in the statement var <- runif (10) < 0.5?

* Logical
* Integer
* Character
* List


### Lecture 2a  

Which of the following equation represents the sensitivity of a test?

* sensitivity = number of true positives / number with disease
* sensitivity = number of true negatives / number without disease
* sensitivity = number with disease / total population
* sensitivity = number of true positives / number of true negatives


### Lecture 2b  

Poisson Probability Distribution is a type of 

* Discrete Probability Distribution
* Continuous Probability Distribution
* Cumulative distibution
* Random number generation

### Lecture 3a  

Given a matrix

```{r matrix_operations, echo=FALSE}

x <- matrix (1:12,4,3)
x
```

what is the output of the statement __x[1, ]__

* [1] 1 5 9
* [1] 1
* [1] 1 2 3 4
* System generates a syntax error

### Lecture 3b   

Given a matrix A 


```{r matrix1, echo=FALSE}
x <- matrix (1:12,4,3)
x
```

what is the output of A * Transpose(A)

*
```{r matrix_operation, echo=FALSE}
x <- matrix (1:12,4,3)
trans <- t(x)
x %*% trans
```

*
```{r matrix2, echo=FALSE}
diag(nrow=4)
```

* [1] 1 2 3 4
* System generates a syntax error


### Lecture 4a  

To find the square of each number from 1 to N, which of the following is the fastest approach


*
x <- 1:N
y <- x^2
  
*
y <- numeric()
for (i in 1:N) y[i] <- i^2

*
y <- numeric(N)
for (i in 1:N) y[i] <- i^2


### Lecture 4b  




